### 2017-10-15 README.Rmd
Add profiles vignette
Update pkgdown site

Infer: An R package for tidyverse-friendly statistical inference

@@

### Hypothesis tests
![h-test diagram](figs/ht-diagram.png)

@@

One numerical variable (mean)

@@

One numerical variable (median)

@@

One numerical variable (standard deviation)

@@

One categorical (2 level) variable

@@

Two categorical (2 level) variables

@@

One categorical (>2 level) - GoF

@@

Two categorical (>2 level) variables

@@

One numerical variable one categorical (2 levels) (diff in means)

@@

One numerical variable one categorical (2 levels) (diff in medians)

@@

One numerical one categorical (>2 levels) -  ANOVA

@@

Two numerical vars - SLR

@@

### Confidence intervals

One numerical (one mean)

@@

One numerical (one median)

@@

One numerical (standard deviation)

@@

One categorical (one proportion)

@@

One numerical variable one categorical (2 levels) (diff in means)

@@

Two categorical variables (diff in proportions)

>>>>

Infer: an R package for tidyverse-friendly statistical inference

@@

## Hypothesis tests
![](figs/ht-diagram.png)

@@

### One numerical variable (mean)

@@

### One numerical variable (median)

@@

### One numerical variable (standard deviation)

@@

### One categorical (2 level) variable

@@

### Two categorical (2 level) variables

@@

### One categorical (>2 level) - GoF

@@

### Two categorical (>2 level) variables

@@

### One numerical variable, one categorical (2 levels) (diff in means)

@@

### One numerical variable one categorical (2 levels) (diff in medians)

@@

### One numerical one categorical (>2 levels) -  ANOVA

@@

### Two numerical vars - SLR

@@

## Confidence intervals

### One numerical (one mean)

@@

### One numerical (one median)

@@

### One numerical (standard deviation)

@@

### One categorical (one proportion)

@@

### One numerical variable one categorical (2 levels) (diff in means)

@@

### Two categorical variables (diff in proportions)
